Demo arXiv template

### 2022-10-24 paper/paper.qmd
more on the tidy data paragraph

As a programming language for data analysis, R provides a scripted environment for users to experiment with data without the complex abstraction a typical programming language requires. 
The flexible and intuitive workflow is paramount for data analysis since in a data analysis project, the full workflow of how data should be processed from the raw data to the final results is usually only consolidated till the end of the project and analysts need the freedom to quickly experiment with different ideas when working with data.
This approach to data analysis is enhanced by the tidyverse suite where a collection of R packages are built for data science under the concept of tidy data. 
The tidy data principle [@wickham_tidy_2014] prescribes three simple rules for structuring tabular data: 1) Each variable forms a column, 2) Each observation forms a row, and; 3) Each type of observational unit forms a table.
The packages built in the tidyverse suite provide operations that are direct actions on the data and users, even new users, can easily read from the code on what has been performed and what to expect after each operation. 
Researchers and analysts have a similar need for an intuitive and flexible process to construct indices since a similar workflow occurs where researchers experiment with many different indices, discover issues with the current ones, and experiment with potential ideas before finally arrive at a solution.

<!-- Researchers working on index construction should consider adopt a workflow where operations on data can be clearly reflected by the code while flexible to experiment  -->

>>>>

As a scripted language for data analysis, R provides a interactive environment for users to code with data without the abstraction a typical programming language requires. 
This flexible environment is paramount for data analysis since in practice, data analysis involves trials and errors on different steps to solve the problems.
Analysts need the freedom to quickly experiment with different ideas when working with data.
The tidyverse suite provides a collection of R package for conducting data analysis.
These tools directly operate on data, and users, even new users, can easily read from the code on what operation is performed on the data and what to expect as the output.
All of these are built upon a simple prior knowledge of the tidy data principle [@wickham_tidy_2014], which prescribes three rules for structuring tabular data: 1) Each variable forms a column, 2) Each observation forms a row, and; 3) Each type of observational unit forms a table.

Constructing indices also involves this working pattern of trails and errors on different options before finding the final solution. A tidy workflow will give researchers more flexibility to tune the steps as they wish and while maintain a readable and intuitive code base.

<!-- While data can be arranged in various different ways, maintaining a fixed representation gives a predictable output of operations on data.  -->

<!-- Only when each step in the workflow has been mapped out, do data analysts need to consider those abstract concept of object oriented programming and functional programming to help them design the workflow.  -->
<!-- how raw data should be processed to the final results can only be consolidated when  -->

### 2022-10-24 paper/paper.tex
more on the tidy data paragraph

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden, boxrule=0pt, breakable, sharp corners]}{\end{tcolorbox}}\fi

@@

As a programming language for data analysis, R provides a scripted
environment for users to experiment with data without the complex
abstraction a typical programming language requires. The flexible and
intuitive workflow is paramount for data analysis since in a data
analysis project, the full workflow of how data should be processed from
the raw data to the final results is usually only consolidated till the
end of the project and analysts need the freedom to quickly experiment
with different ideas when working with data. This approach to data
analysis is enhanced by the tidyverse suite where a collection of R
packages are built for data science under the concept of tidy data. The
tidy data principle (Wickham 2014) prescribes three simple rules for
structuring tabular data: 1) Each variable forms a column, 2) Each
observation forms a row, and; 3) Each type of observational unit forms a
table. The packages built in the tidyverse suite provide operations that
are direct actions on the data and users, even new users, can easily
read from the code on what has been performed and what to expect after
each operation. Researchers and analysts have a similar need for an
intuitive and flexible process to construct indices since a similar
workflow occurs where researchers experiment with many different
indices, discover issues with the current ones, and experiment with
potential ideas before finally arrive at a solution.

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, breakable, boxrule=0pt, frame hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden]}{\end{tcolorbox}}\fi

@@

As a scripted language for data analysis, R provides a interactive
environment for users to code with data without the abstraction a
typical programming language requires. This flexible environment is
paramount for data analysis since in practice, data analysis involves
trials and errors on different steps to solve the problems. Analysts
need the freedom to quickly experiment with different ideas when working
with data. The tidyverse suite provides a collection of R package for
conducting data analysis. These tools directly operate on data, and
users, even new users, can easily read from the code on what operation
is performed on the data and what to expect as the output. All of these
are built upon a simple prior knowledge of the tidy data principle
(Wickham 2014), which prescribes three rules for structuring tabular
data: 1) Each variable forms a column, 2) Each observation forms a row,
and; 3) Each type of observational unit forms a table.

Constructing indices also involves this working pattern of trails and
errors on different options before finding the final solution. A tidy
workflow will give researchers more flexibility to tune the steps as
they wish and while maintain a readable and intuitive code base.
